Approximation as Differentiation

### 2025-05-06 appendix/notes.tex
Preliminaries.
Some cleanup/better org.
Tangent map.
Move syntax fig to notes.
Move auto-diff to after definition of FinVect.
Move LatGal and FinVect to after section on biproducts/semi-additive categories.
Auto-diff separate.
Sync summary of notes.

Covered so far:
\begin{itemize}
\item $\CMon$-enriched categories, including enriched functors and enriched Yoneda embedding (\secref{cmon-enriched})
\item biproducts and semi-additive categories (\secref{biproduct})
\item category $\Fam(I,\cat{C})$ of $I$-indexed families of objects of $\cat{C}$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{\cat{C}}F$ and category of families $\Fam(\cat{C})$
(\secref{grothendieck})
\item Examples of useful semi-additive categories (\secref{useful-semi-additive-categories}):
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FinVect_F$ of finite-dimensional vector spaces over a field $F$
   (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\end{itemize}

@@

\input{appendix/notes/notation}
\input{appendix/notes/cmon-enriched}
\input{appendix/notes/biproduct}
\input{appendix/notes/fam}
\input{appendix/notes/set-indexed-product}
\input{appendix/notes/grothendieck}
\input{appendix/notes/useful-semi-additive-categories}

% \input{appendix/notes/language}

>>>>

Covered so far:
\begin{itemize}
\item automatic differentiation (\secref{auto-diff})
\item $\CMon$-enriched categories, including enriched functors and enriched Yoneda embedding (\secref{cmon-enriched})
\item biproducts and semi-additive categories (\secref{biproduct})
\item useful semi-additive categories (\secref{useful-semi-additive-categories}):
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FinVect_F$ of finite-dimensional vector spaces over a field $F$
   (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\item category $\Fam(I,\cat{C})$ of $I$-indexed families of objects of $\cat{C}$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{\cat{C}}F$ and category of families $\Fam(\cat{C})$
(\secref{grothendieck})
\item useful categories of families for automatic approximation
(\secref{galois-slicing-auto-diff-via-grothendieck}):
   \begin{itemize}
      \item Galois slicing via $\Fam(\LatGal)$ (\secref{galois-slicing-auto-diff-via-grothendieck:galois-slicing})
      \item automatic differentiation via $\Fam(\FinVect)$ (\secref{galois-slicing-auto-diff-via-grothendieck:auto-diff})
   \end{itemize}
\end{itemize}

@@

\input{appendix/notes/preliminaries}
\input{appendix/notes/auto-diff}
\input{appendix/notes/cmon}
\input{appendix/notes/cmon-enriched}
\input{appendix/notes/biproduct}
\input{appendix/notes/useful-semi-additive-categories}
\input{appendix/notes/fam}
\input{appendix/notes/set-indexed-product}
\input{appendix/notes/grothendieck}
\input{appendix/notes/auto-diff-galois-slicing-via-grothendieck}
\input{appendix/notes/language}
